---
title: "R Programming: Zero to Pro (14)"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

### Lesson 14

### Exercise 14

1. Generate a histogram for the variable `carat` in the `diamonds` dataset, with 10 bins. 

```{r hist-diamonds, exercise=TRUE}

```

```{r hist-diamonds-solution}
library(tidyverse)
ggplot(data = diamonds) + 
  geom_histogram(mapping = aes(x = carat), bins = 10)
```

2. Generate a histogram for the variable `carat` in the `diamonds` dataset with binwidth = 0.5, and set the breaks on the x-axis to start at -0.25 and end at 5, with increment 0.5. 

```{r break, exercise=TRUE}

```

```{r break-solution}
ggplot(data = diamonds) + 
  geom_histogram(mapping = aes(x = carat), binwidth = 0.5) +
   scale_x_continuous(breaks = seq(from = -0.25, to = 5, by = 0.5))
```


3. Generate a histogram for the variable `carat` with 10 bins, and map the variable `cut` to the fill aesthetic.

```{r hist-fill, exercise=TRUE}

```

```{r hist-fill-solution}
ggplot(data = diamonds) + 
  geom_histogram(mapping = aes(x = carat, fill = cut), bins = 10)
```

4. Generate a histogram for the variable `carat` with 10 bins, and show the proportion for different values of `color` inside each bin.

```{r color, exercise=TRUE}

```

```{r color-solution}
ggplot(data = diamonds) + 
  geom_histogram(mapping = aes(x = carat, fill = color), position = 'fill', bins = 10)
```



