---
title: "R Programming: Zero to Pro"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

### Lesson 9: ggplot2: Smoothline Fit via geom_smooth
![](https://youtu.be/_7iSlYnDY5E)

### Exercise 9

1. Create a smoothline fit of `displ`(on the x-axis) and `hwy`(on the y-axis) using the  `mpg` dataset without confidence interval around the smoothline fit.

```{r se, exercise=TRUE}

```

```{r se-solution}
library(tidyverse)
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy), se = FALSE)
```

2. Using the `mpg` dataset, create smoothline fits of `displ`(on the x-axis) and `hwy`(on the y-axis) with different colors depending on the value of variable `drv`.  

```{r color, exercise=TRUE}

```

```{r color-solution}
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, color = drv))
```

3. Using the `mpg` dataset, create smoothline fits of `displ`(on the x-axis) and `hwy`(on the y-axis) with green color and different linetypes, depending on the value of variable `drv`.  

```{r linetype, exercise=TRUE}

```

```{r linetype-solution}
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, linetype = drv), color = "green")
```

