---
title: "R Programming: Zero to Pro"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

### Lesson 8 Aesthetics in Scatterplots (III) 

### Exercise 8

1. In `mpg` dataset, among the variables `model`, `year`, `cyl`, and `trans`,

```{r d-plus-e, echo=FALSE}
quiz(
  question("how many are continuous?",
    answer("0"),
    answer("1"),
    answer("2", correct = T),
    answer("3")
  ),
    caption = NULL
)
```

2. Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and map `displ` to the `color` aesthetic.

```{r displ, exercise=TRUE}

```

```{r displ-solution}
library(tidyverse)
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = displ))
```

3. Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and map `displ` to the `color` aesthetic, map low values of displ to yellow and high values to blue, map `hwy` to the `size` aesthetic, and use `shape = 2` for all points. 


```{r color_scale, exercise=TRUE}

```

```{r color_scale-solution}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty, color = displ, size = hwy), shape = 2) +
  scale_color_continuous(low = "yellow", high = "blue")
```

4. Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and map a logical vector`class == "compact"` to the `shape` aesthetic, and use `size = 2` for all points..


```{r logical, exercise=TRUE}

```

```{r logical-solution}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty, shape = class == "compact"), size = 2)
```
