---
title: "R Programming: Zero to Pro"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```
```{r prepare-hwys}
small_displ <- mpg$displ < 3
hwy1 <- mpg$hwy[small_displ] 
big_displ <- mpg$displ >= 3
hwy2 <- mpg$hwy[big_displ] 
```
### Exercise 4

Using the `mpg` data set, we want to compare highway miles per gallon (`hwy`) on the cars with certain engine displacement (`displ`).

1. Create a vector variable `hwy1` that contains the `hwy` for all the cars with `displ` smaller than 3 and calculate its summary.

```{r hwy1, exercise=TRUE}

```

```{r hwy1-solution}
small_displ <- mpg$displ < 3
hwy1 <- mpg$hwy[small_displ] 
summary(hwy1)
```

2. Create a vector variable `hwy2` that contains the `hwy` for all the cars with `displ` larger than or equal to 3 and calculate its summary.

```{r hwy2, exercise=TRUE}

```

```{r hwy2-solution}
big_displ <- mpg$displ >= 3
hwy2 <- mpg$hwy[big_displ] 
summary(hwy2)
```


3. Find the differences in mean and median for `hwy1` and `hwy2`. 


```{r hwydiff, exercise=TRUE, exercise.setup = "prepare-hwys"}

```

```{r hwydiff-solution}
mean(hwy1) - mean(hwy2)
median(hwy1) - median(hwy2)
```

