---
title: "R Programming: Zero to Pro"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

### Exercise 6

#### Creating a ggplot with aesthetics.

1. Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and map `drv` to the `color` aesthetic.

```{r color, exercise=TRUE}

```

```{r color-solution}
library(tidyverse)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty, color = drv))
```

2. Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and map `drv` to the `size` aesthetic.

```{r size, exercise=TRUE}

```

```{r size-solution}
library(tidyverse)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty, size = drv))
```

3. Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and map `drv` to the `shape` aesthetic.

```{r shape, exercise=TRUE}

```

```{r shape-solution}
library(tidyverse)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty, shape = drv))
```

#### Bonus Questions

The following questions may be a bit difficult. Please feel free to look at the solutions if needed and we will review them in Lesson 7. 

4. (Map the same variable to multiple aesthetics) Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and map `drv` to the `color` and `shape` aesthetics.

```{r all, exercise=TRUE}

```

```{r all-solution}
library(tidyverse)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty, color = drv, shape = drv))
```


5. (Map different variables to different aesthetics) Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, where we map `drv` to the `color` and map `fl` to `shape`.

```{r color_shape, exercise=TRUE}

```

```{r color_shape-solution}
library(tidyverse)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty, color = drv, shape = fl))
```

