---
title: "R Programming: Zero to Pro"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = TRUE)
```

### Lesson 7: ggplot2: Aesthetics in scatterplots (II)

![](https://youtu.be/gHW8yg9rhC0)



#### Creating ggplots with aesthetics.

1. Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and use `green` for all points.

```{r blue, exercise=TRUE}

```

```{r blue-solution}
library(tidyverse)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty), color = "green")
```

2. Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and map `drv` to the `size` aesthetic, and use `green` for all points.

```{r size_green, exercise=TRUE}

```

```{r size_green-solution}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty, size = drv), color = "green")
```

3. Create a scatterplot of `displ`(on the x-axis) and `cty`(on the y-axis) using the  `mpg` dataset, and map `drv` to the `shape` aesthetic, map `class` to the `color` aesthetic, and use `size=2` for all points.

```{r shape_color_size_2, exercise=TRUE}

```

```{r shape_color_size_2-solution}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = cty, shape = drv, color = class), size = 2)
```


