---
title: "R Programming: Zero to Pro (13)"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

### Lesson 13

### Exercise 13

1. Create a length-8 equal-spaced vector from 20 to 6. What is the increment of the numeric vector?

```{r prop, exercise=TRUE}

```

```{r prop-solution}
seq(from = 20, to = 6, length.out = 8)
#The increment number is -2.
```

2. Create a scatterplot between `depth`(on the x-axis) and `price`(on the y-axis) using the `diam2` data, and set the breaks to start at 55 and end at 65 with increment of 5 on the x axis. 
(Hint: you can use the following code to create `diam2`: 
diam2 <- diamonds %>% filter(color == "D") )

```{r dodge, exercise=TRUE}

```

```{r dodge-solution}
library(tidyverse)
diam2 <- diamonds %>% filter(color == "D") 
ggplot(data = diam2) + geom_point(mapping = aes(x = depth, y = price)) +
 scale_x_continuous(breaks = seq(from = 55, to = 65, by = 5)) 
```

3. Zoom in the above scatterplot to a region that only shows the points with `depth` between 60 and 65 and `price` between 10K and 15K

```{r limit, exercise=TRUE}

```

```{r limit-solution}
ggplot(data = diam2) + geom_point(mapping = aes(x = depth, y = price)) +
coord_cartesian(xlim = c(60, 65), ylim = c(10000, 15000))
```

